\textbf{universal corpus}

### 2014-04-25 docs/computEL-final/concl.tex
Tidied tex files
(I have removed some commented sections that are unlikely to be included
again.  They are of course still available in the old commits.)
added link to new repo

SeedLing will be made available initially through the websites of the authors, as we have yet to properly address the question of long-term access; we welcome ideas or collaborations along these lines. In addition, we are releasing a Python API which allows programmatic access to the data and is easily compatible with the analysis tools available from the Natural Language ToolKit \cite{BirdKleinLoper09}. The API also facilitates access to information from both Ethnologue and WALS: a user can extract information about languages, language classification, endangerment status, typological features, and so on. Finally, we will make our clustering scripts freely available.

% To demonstrate the utility of this resource, we used the data to perform language clustering, which gave promising results.

>>>>

SeedLing will be made available initially through the websites of the authors, as we have yet to properly address the question of long-term access; we welcome ideas or collaborations along these lines. In addition, we are releasing a Python API which allows programmatic access to the data and is easily compatible with the analysis tools available from the Natural Language ToolKit \cite{BirdKleinLoper09} \footnote{\url{https://github.com/alvations/SeedLing}}. The API also facilitates access to information from both Ethnologue and WALS: a user can extract information about languages, language classification, endangerment status, typological features, and so on. Finally, we will make our clustering scripts freely available.
